---
title: "Custom learners for calibrated DML"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Custom learners for calibrated DML}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(calibratedDML)
source("tutorial_helpers.R")
binary <- make_binary_fixture()
```

This vignette shows the supported learner-specification paths in the R interface:

- built-in learner strings
- custom model specification lists with `fit` and `predict`
- optional `SuperLearner` backends
- optional `sl3` learners

## Built-in learner strings

```{r}
fit_builtin <- calibrated_dml(
  data = binary$data,
  outcome = "Y",
  treatment = "A",
  covariates = c("W1", "W2"),
  control_level = 0,
  outcome_model = "lm",
  treatment_model = "multinom",
  inference = "wald",
  n_folds = 3,
  seed = 4
)

confint(fit_builtin, type = "contrast")
```

## Custom model specification lists

Custom specs are lists with:

- `kind = "regression"` or `kind = "classification"`
- a `fit(x, y, weights)` function
- a `predict(model_fit, newx)` function

```{r}
fit_custom <- calibrated_dml(
  data = binary$data,
  outcome = "Y",
  treatment = "A",
  covariates = c("W1", "W2"),
  control_level = 0,
  outcome_model = make_regression_spec(),
  treatment_model = make_binary_classification_spec(),
  inference = "wald",
  n_folds = 3,
  seed = 5
)

confint(fit_custom, type = "contrast")
```

For multi-arm treatment, a custom classification model should return one probability column per treatment level.

## Optional `SuperLearner` backends

```{r}
if (requireNamespace("SuperLearner", quietly = TRUE)) {
  sl_spec <- list(SL.library = c("SL.mean", "SL.glm"))
  fit_sl <- calibrated_dml(
    data = binary$data,
    outcome = "Y",
    treatment = "A",
    covariates = c("W1", "W2"),
    control_level = 0,
    outcome_model = sl_spec,
    treatment_model = sl_spec,
    inference = "wald",
    n_folds = 3,
    seed = 6
  )
  confint(fit_sl, type = "contrast")
} else {
  "Install SuperLearner to run the optional SuperLearner example."
}
```

## Optional `sl3` learners

```{r}
if (requireNamespace("sl3", quietly = TRUE)) {
  learners <- calibratedDML::default_learners()
  fit_sl3 <- calibrated_dml(
    data = binary$data,
    outcome = "Y",
    treatment = "A",
    covariates = c("W1", "W2"),
    control_level = 0,
    outcome_model = learners[[2]],
    treatment_model = learners[[2]],
    stratify = c("outcome", "treatment"),
    inference = "wald",
    n_folds = 3,
    seed = 7
  )
  confint(fit_sl3, type = "contrast")
} else {
  "Install sl3 to run the optional sl3 example."
}
```

When nuisance estimation already happens elsewhere, the cleaner route is often to skip learner integration entirely and use `calibrated_dml_from_nuisances()`.
