---
title: "Standard calibrated DML workflows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Standard calibrated DML workflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(calibratedDML)
source("tutorial_helpers.R")
```

This vignette shows the standard calibrated DML workflow from raw data. It covers binary and multi-arm treatments, the main result tables, and the three supported inference modes.

## Fit from raw data

```{r}
binary <- make_binary_fixture()

fit_wald <- calibrated_dml(
  data = binary$data,
  outcome = "Y",
  treatment = "A",
  covariates = c("W1", "W2"),
  control_level = 0,
  outcome_model = "lm",
  treatment_model = "multinom",
  inference = "wald",
  n_folds = 3,
  seed = 1
)

summary(fit_wald)
```

The fitted object stores arm means, treatment-versus-control contrasts, calibrated nuisance matrices, and the nuisance source. The shortest result views are `summary(fit_wald)` and `confint(fit_wald)`.

```{r}
confint(fit_wald, type = "contrast")
```

## Choose the inference layer explicitly

```{r}
fit_bootstrap <- calibrated_dml(
  data = binary$data,
  outcome = "Y",
  treatment = "A",
  covariates = c("W1", "W2"),
  control_level = 0,
  outcome_model = "lm",
  treatment_model = "multinom",
  inference = "bootstrap",
  bootstrap_reps = 25,
  n_folds = 3,
  seed = 2
)

confint(fit_bootstrap, type = "contrast")
```

For larger analyses, increase `bootstrap_reps` or `jackknife_folds`. The tutorial keeps them small so the vignette renders quickly.

## Multi-arm treatment with control contrasts

```{r}
multiarm <- make_multiarm_fixture()

fit_multiarm <- calibrated_dml(
  data = multiarm$data,
  outcome = "Y",
  treatment = "A",
  covariates = c("W1", "W2"),
  control_level = 0,
  outcome_model = "lm",
  treatment_model = "multinom",
  inference = "jackknife",
  jackknife_folds = 5,
  n_folds = 3,
  seed = 3
)

summary(fit_multiarm)
```

This standard interface is the right starting point when the package should fit nuisance models internally from raw data.
