---
title: "Supplied nuisance matrices"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Supplied nuisance matrices}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(calibratedDML)
source("tutorial_helpers.R")
```

This vignette shows the supplied-nuisance workflow. Use it when cross-fitted outcome and treatment nuisance estimates already exist and only calibration, debiasing, and inference should be run here.

## Binary treatment from supplied nuisance matrices

```{r}
binary <- make_binary_fixture()

fit_binary <- calibrated_dml_from_nuisances(
  A = binary$A,
  Y = binary$Y,
  mu_mat = binary$mu_mat,
  pi_mat = binary$pi_mat,
  control_level = 0,
  inference = "bootstrap",
  bootstrap_reps = 25
)

summary(fit_binary)
```

Each nuisance matrix should have one row per observation and one column per treatment level.

## Multi-arm treatment with explicit level alignment

```{r}
multiarm <- make_multiarm_fixture()

mu_perm <- multiarm$mu_mat[, c("2", "0", "1")]
pi_perm <- multiarm$pi_mat[, c("2", "0", "1")]

fit_multiarm <- calibrated_dml_from_nuisances(
  A = multiarm$A,
  Y = multiarm$Y,
  mu_mat = mu_perm,
  pi_mat = pi_perm,
  control_level = 0,
  treatment_levels = c(0, 1, 2),
  inference = "wald"
)

summary(fit_multiarm)
```

The explicit `treatment_levels` argument is useful whenever matrices come from an external pipeline and you want to lock the arm ordering down.
